---
title: "STATISTICS 2023-2024"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      primary: '#77253D'
      bootswatch: default
    orientation: rows
    vertical_layout: scroll
    logo: "www/logo-nba.png"
resource_files:
- "www/logo-atl.png"
- "www/logo-bos.png"
- "www/logo-bkn.png"
- "www/logo-cha.png"
- "www/logo-chi.png"
- "www/logo-cle.png"
- "www/logo-dal.png"
- "www/logo-den.png"
- "www/logo-det.png"
- "www/logo-gsw.png"
- "www/logo-hou.png"
- "www/logo-ind.png"
- "www/logo-lac.png"
- "www/logo-lal.png"
- "www/logo-mem.png"
- "www/logo-mia.png"
- "www/logo-mil.png"
- "www/logo-min.png"
- "www/logo-nop.png"
- "www/logo-nyk.png"
- "www/logo-okc.png"
- "www/logo-orl.png"
- "www/logo-phi.png"
- "www/logo-phx.png"
- "www/logo-por.png"
- "www/logo-sac.png"
- "www/logo-sas.png"
- "www/logo-tor.png"
- "www/logo-uta.png"
- "www/logo-was.png"
---

```{r setup, include=FALSE}
# Packages
library(dplyr)
library(readr)
library(shiny)
library(flexdashboard)
library(ggplot2)
library(plotly)
library(htmltools)

# Load data
players <- read_csv("Clean/Players_2023-24.csv")
east <- read_csv("Clean/East_2023-24.csv")
west <- read_csv("Clean/West_2023-24.csv")
```


Sidebar {.sidebar}
=======================================================================
```{r}
selectInput("teams",
            "SELECT A TEAM",
            choices = sort(unique(players$TEAM_NAME)),
            selected = "ATL")

selectInput("players",
            "SELECT A PLAYER",
            choices = NULL)

# Observe selection on Team input
observe({
  team_selected <- input$teams
    
  # Check if team_selected is NULL or empty, return early if it is
  if (is.null(team_selected) || team_selected == "") {
    return()
  }
  
  players_list <- players %>% 
    filter(TEAM_NAME == team_selected) %>% 
    select(PLAYER_NAME)
  
  players_list <-  sort(unique(players_list$PLAYER_NAME))
  
  # Update the Players based on the team selected,
  # setting the choices to the relevant subset from the players list
  updateSelectInput(session, 
                    "players",
                    label = "SELECT A PLAYER",
                    choices = players_list,
                    selected = players_list[1])
})

roster <- reactive({
  players %>% filter(TEAM_NAME == input$teams)
})

current <- reactive({
  players %>% filter(PLAYER_NAME == input$players)
})


renderImage({
  # Obtain the selected team name
  selected_team <- tolower(unique(roster()$TEAM_ABBREVIATION))
  
  list(src = paste0("www/logo-", selected_team, ".png"),
       contentType = "image/png",
       width = "auto",
       height = "auto")
  }, deleteFile = F)

create_stat_plot <- function(stat) {
  df <- reactive({
    roster() %>% 
      mutate(PlayerSelected = if_else(PLAYER_NAME == input$players, 
                                      "Selected", "Not Selected"),
             stats = .data[[stat]]) %>%
      arrange(desc(stats)) %>% 
      mutate(PLAYER_NAME = factor(PLAYER_NAME, levels = rev(unique(PLAYER_NAME))))
  })
  
  
  ggplot(df(), aes(x = PLAYER_NAME, y = stats, fill = PlayerSelected)) +
    geom_bar(stat = "identity", alpha = .6, width = .5, show.legend = F) +
    scale_fill_manual(values = c("Selected" = "#6F263D", "Not Selected" = "#1d428a")) +
    coord_flip() +
    labs(x = NULL, y = NULL) +
    theme_minimal()
  
  # return(ggplotly(p, tooltip = "y"))
  # Create a reprex and open an issue on git hub for plotly not being consistent.
}

create_top_10 <- function(stat) {
  df <- reactive({
    players %>% 
      mutate(stats = .data[[stat]]) %>%
      arrange(desc(stats)) %>% 
      mutate(PLAYER_NAME = factor(PLAYER_NAME, levels = rev(unique(PLAYER_NAME)))) %>% 
      slice_head(n = 10)
  })
  
  
  q <- ggplot(df(), aes(x = PLAYER_NAME, y = stats)) +
    geom_bar(stat = "identity", fill = "#1d428a", alpha = .6, width = .5, show.legend = F) +
    coord_flip() +
    labs(x = NULL, y = NULL) +
    theme_minimal() 
  
  return(ggplotly(q, tooltip = "y"))
}

create_ranking <- function(conf) { 
  df <- reactive({
    conf %>% 
      arrange(W_PCT) %>% 
      mutate(TeamSelected = case_when(row_number() %in% c(1:5) ~ "Eliminated",
                                      row_number() %in% c(6:9) ~ "Play-in",
                                      row_number() %in% c(10:15) ~ "Playoffs"),
             TEAM_NAME = factor(TEAM_NAME, levels = TEAM_NAME))
  })
  
  t <- ggplot(df(), aes(x = TEAM_NAME, y = W_PCT, fill = TeamSelected)) +
    geom_bar(stat = "identity", alpha = .6, width = .5, show.legend = F) +
    scale_fill_manual(values = c("Playoffs" = "#1d428a", 
                                 "Play-in" = "#6F263D", 
                                 "Eliminated" = "#212121")) +
    coord_flip() +
    labs(x = NULL, y = "Win Percentage") +
    theme_minimal() 
  
  return(ggplotly(t, tooltip = "y"))
}
```

PLAYER SUMMARY 
=======================================================================

Row
-----------------------------------------------------------------------

### Team 
```{r}
renderValueBox({
  valueBox(
    value = current()$TEAM_ABBREVIATION,
    caption = "Team",
    icon = "fa-shirt",
    color = "#1d428a"
  )
})
```


### Age 
```{r}
renderValueBox({
  valueBox(
    value = current()$AGE,
    caption = "Years old",
    icon = "fa-calendar",
    color = "#1d428a"
  )
})
```


### Minutes per Game 
```{r}
renderValueBox({
  valueBox(
    value = current()$MIN,
    caption = "Minutes Per Game",
    icon = "fa-clock",
    color = "#1d428a"
  )
})
```


### Games Played
```{r}
renderValueBox({
  valueBox(
    value = current()$GP,
    caption = "Games Played",
    icon = "fa-calendar-check",
    color = "#1d428a"
  )
})
```


### Points per Game 
```{r}
renderValueBox({
  valueBox(
    value = current()$PTS,
    caption = "Points Per Game",
    icon = "fa-basketball",
    color = "#1d428a"
  )
})
```


Row
-----------------------------------------------------------------------

### Field Goal Percentage
```{r}
renderGauge({
  gauge(value = 100 * current()$FG_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(40, 100), warning = c(20, 40), danger = c(0, 20),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


### Free Throw Percentage
```{r}
renderGauge({
  gauge(value = 100 * current()$FT_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(75, 100), warning = c(60, 75), danger = c(0, 60),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


### 3 Point Percentage
```{r}
renderGauge({
  gauge(value = 100 * current()$FG3_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(35, 100), warning = c(20, 35), danger = c(0, 20),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


Row
-----------------------------------------------------------------------

### Assists per Game 
```{r}
renderValueBox({
  valueBox(
    value = current()$AST,
    caption = "Assists Per Game",
    icon = "fa-handshake-angle",
    color = "#1d428a"
  )
})
```


### Rebounds per Game 
```{r}
renderValueBox({
  valueBox(
    value = current()$REB,
    caption = "Rebounds Per Game",
    icon = "fa-hands-holding-circle",
    color = "#1d428a"
  )
})
```


### Blocks per Game
```{r}
renderValueBox({
  valueBox(
    value = current()$BLK,
    caption = "Blocks Per Game",
    icon = "fa-hand-point-up",
    color = "#1d428a"
  )
})
```


### Steals per Game
```{r}
renderValueBox({
  valueBox(
    value = current()$STL,
    caption = "Steals Per Game",
    icon = "fa-people-robbery",
    color = "#1d428a"
  )
})
```


### Turnovers per Game
```{r}
renderValueBox({
  valueBox(
    value = current()$TOV,
    caption = "Turnovers Per Game",
    icon = "fa-person-walking-arrow-loop-left",
    color = "#1d428a"
  )
})
```

Row {.tabset}
-----------------------------------------------------------------------

### Points Comparison
```{r}
renderPlot({
  create_stat_plot("PTS")
})
```


### Assists Comparison
```{r}
renderPlot({
  create_stat_plot("AST")
})
```


### Rebounds Comparison
```{r}
renderPlot({
  create_stat_plot("REB")
})
```



TEAM SUMMARY {data-navmenu="Under Development"}
=======================================================================

This tab is currently under development. Stay tuned!

Row
-----------------------------------------------------------------------

OFFENSE {data-navmenu="Under Development"}
=======================================================================

This tab is currently under development. Stay tuned!

Row
-----------------------------------------------------------------------

<!-- ### Minutes per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$MIN, -->
<!--     caption = "Minutes Per Game", -->
<!--     icon = "fa-clock", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### Points per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$PTS, -->
<!--     caption = "Points Per Game", -->
<!--     icon = "fa-basketball", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### Field Goal Attempted per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$FGA, -->
<!--     caption = "FG Attempted Per Game", -->
<!--     icon = "fa-dribbble", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### 3 Points Attempted per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$FG3A, -->
<!--     caption = "3 Pts Attempted Per Game", -->
<!--     icon = "fa-hands-asl-interpreting", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### Free Throws Attempted per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$FTA, -->
<!--     caption = "FT Attempted Per Game", -->
<!--     icon = "fa-ring", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


DEFENSE {data-navmenu="Under Development"}
=======================================================================

This tab is currently under development. Stay tuned!

Row
-----------------------------------------------------------------------

LEADERS
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### Points
```{r}
renderPlotly({
  create_top_10("PTS")
})
```


### Assists
```{r}
renderPlotly({
  create_top_10("AST")
})
```


### Turnovers
```{r}
renderPlotly({
  create_top_10("TOV")
})
```


### Rebounds
```{r}
renderPlotly({
  create_top_10("REB")
})
```


### Blocks
```{r}
renderPlotly({
  create_top_10("BLK")
})
```


### Steals
```{r}
renderPlotly({
  create_top_10("STL")
})
```


Row
-----------------------------------------------------------------------

### Western Ranking
```{r}
renderPlotly({
  create_ranking(west)
})
```


### Eastern Ranking
```{r}
renderPlotly({
  create_ranking(east)
})
```

