---
title: "STATISTICS 2024-2025"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      primary: '#77253D'
      bootswatch: default
    orientation: rows
    vertical_layout: scroll
    logo: "www/logo-nba.png"
resource_files:
- "www/logo-atl.png"
- "www/logo-bos.png"
- "www/logo-bkn.png"
- "www/logo-cha.png"
- "www/logo-chi.png"
- "www/logo-cle.png"
- "www/logo-dal.png"
- "www/logo-den.png"
- "www/logo-det.png"
- "www/logo-gsw.png"
- "www/logo-hou.png"
- "www/logo-ind.png"
- "www/logo-lac.png"
- "www/logo-lal.png"
- "www/logo-mem.png"
- "www/logo-mia.png"
- "www/logo-mil.png"
- "www/logo-min.png"
- "www/logo-nop.png"
- "www/logo-nyk.png"
- "www/logo-okc.png"
- "www/logo-orl.png"
- "www/logo-phi.png"
- "www/logo-phx.png"
- "www/logo-por.png"
- "www/logo-sac.png"
- "www/logo-sas.png"
- "www/logo-tor.png"
- "www/logo-uta.png"
- "www/logo-was.png"
---

```{r setup, include=FALSE}
# Packages
library(dplyr)
library(readr)
library(shiny)
library(flexdashboard)
library(ggplot2)
library(plotly)
library(htmltools)
library(ggrepel)

# Load helper functions for graphs
eval(parse("helpers.R", encoding = "UTF-8"))

# Load data
players <- read_csv("Clean/Players_2024-25.csv") # All players stats
east <- read_csv("Clean/East_2024-25.csv") # Eastern conference teams stats
west <- read_csv("Clean/West_2024-25.csv") # Western conference teams stats
```


Sidebar {.sidebar}
=======================================================================
```{r}
# A field to select an NBA team
selectInput("teams",
            "SELECT A TEAM",
            choices = sort(unique(players$TEAM_NAME)),
            selected = "ATL")

# A field to select an NBA player
selectInput("players",
            "SELECT A PLAYER",
            choices = NULL)

# Observe selection on Team input and update Player field with players  
# belonging to the team
observe({
  
  # Get the selected team
  team_selected <- input$teams
    
  # Check if team_selected is NULL or empty, return early if it is
  if (is.null(team_selected) || team_selected == "") {
    return()
  }
  
  # Filter the players data set only on players for the selected team
  players_list <- players %>% 
    filter(TEAM_NAME == team_selected) %>% 
    select(PLAYER_NAME)
  
  # Order them by name (A-Z)
  players_list <-  sort(unique(players_list$PLAYER_NAME))
  
  # Finally, update the Players input with the selected players list
  updateSelectInput(session, 
                    "players",
                    label = "SELECT A PLAYER",
                    choices = players_list,
                    selected = players_list[1])
})

# current players list in the player input
roster <- reactive({
  players %>% filter(TEAM_NAME == input$teams)
})

# Current player selected
current <- reactive({
  players %>% filter(PLAYER_NAME == input$players)
})

# Display the logo of the selected team
renderImage({
  
  # Obtain the selected team abbreviation
  selected_team <- tolower(unique(roster()$TEAM_ABBREVIATION))
  
  # Get the relevant .png file in www folder and display
  list(src = paste0("www/logo-", selected_team, ".png"),
       contentType = "image/png",
       width = "auto",
       height = "auto")
  }, deleteFile = F)

# A field to look for a player's team 
textInput("search", 
          "Search  Player's Team", 
          value = "", 
          placeholder = "Enter name")

renderText({
  
  # Get the matching player name
  found <- players %>% 
    filter(grepl(tolower(input$search), tolower(PLAYER_NAME))) %>% 
    unique()
  
  # Create message to display based on if we have a match or not
  if (nrow(found) != 0 && input$search != "") {
    verbose <- paste0(found$PLAYER_NAME, " plays for ", found$TEAM_NAME)
  } else {
    verbose <- "No matching yet, try to correct the spelling"
  }
  
  # Display message
  verbose
})
```

PLAYER SUMMARY {data-navmenu="SUMMARY"}
=======================================================================

Row
-----------------------------------------------------------------------

### Team 
```{r}
# Which team the player selected belongs to
renderValueBox({
  valueBox(
    value = current()$TEAM_ABBREVIATION,
    caption = "Team",
    icon = "fa-shirt",
    color = "#1d428a"
  )
})
```


### Age 
```{r}
# What's the age of the player selected
renderValueBox({
  valueBox(
    value = current()$AGE,
    caption = "Years old",
    icon = "fa-calendar",
    color = "#1d428a"
  )
})
```


### Minutes per Game 
```{r}
# What's the number of minutes he plays per game
renderValueBox({
  valueBox(
    value = current()$MIN,
    caption = "Minutes Per Game",
    icon = "fa-clock",
    color = "#1d428a"
  )
})
```


### Games Played
```{r}
# What's the number games played 
renderValueBox({
  valueBox(
    value = current()$GP,
    caption = "Games Played",
    icon = "fa-calendar-check",
    color = "#1d428a"
  )
})
```


### Points per Game 
```{r}
# How many points he averages
renderValueBox({
  valueBox(
    value = current()$PTS,
    caption = "Points Per Game",
    icon = "fa-basketball",
    color = "#1d428a"
  )
})
```


Row
-----------------------------------------------------------------------

### Field Goal Percentage
```{r}
# What's his field goal (2 points + 3 points) percentage 
renderGauge({
  gauge(value = 100 * current()$FG_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(40, 100), warning = c(20, 40), danger = c(0, 20),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


### Free Throw Percentage
```{r}
# What's his free throw percentage 
renderGauge({
  gauge(value = 100 * current()$FT_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(75, 100), warning = c(60, 75), danger = c(0, 60),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


### 3 Point Percentage
```{r}
# What's his 3 points percentage 
renderGauge({
  gauge(value = 100 * current()$FG3_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(35, 100), warning = c(20, 35), danger = c(0, 20),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


Row
-----------------------------------------------------------------------

### Assists per Game 
```{r}
# How many assists he averages per game
renderValueBox({
  valueBox(
    value = current()$AST,
    caption = "Assists Per Game",
    icon = "fa-handshake-angle",
    color = "#1d428a"
  )
})
```


### Rebounds per Game 
```{r}
# How many rebounds he averages per game
renderValueBox({
  valueBox(
    value = current()$REB,
    caption = "Rebounds Per Game",
    icon = "fa-hands-holding-circle",
    color = "#1d428a"
  )
})
```


### Blocks per Game
```{r}
# How many blocks he averages per game
renderValueBox({
  valueBox(
    value = current()$BLK,
    caption = "Blocks Per Game",
    icon = "fa-hand-point-up",
    color = "#1d428a"
  )
})
```


### Steals per Game
```{r}
# How many steals he averages per game
renderValueBox({
  valueBox(
    value = current()$STL,
    caption = "Steals Per Game",
    icon = "fa-people-robbery",
    color = "#1d428a"
  )
})
```


### Turnovers per Game
```{r}
# How many turnovers he averages per game
renderValueBox({
  valueBox(
    value = current()$TOV,
    caption = "Turnovers Per Game",
    icon = "fa-person-walking-arrow-loop-left",
    color = "#1d428a"
  )
})
```

Row {.tabset}
-----------------------------------------------------------------------

### Points Comparison
```{r}
# How does his points average compare to his teammates 
renderPlot({
  create_stat_plot("PTS")
})
```


### Assists Comparison
```{r}
# How does his assists average compare to his teammates 
renderPlot({
  create_stat_plot("AST")
})
```


### Rebounds Comparison
```{r}
# How does his rebounds average compare to his teammates 
renderPlot({
  create_stat_plot("REB")
})
```

### Blocks Comparison
```{r}
# How does his blocks average compare to his teammates 
renderPlot({
  create_stat_plot("BLK")
})
```


### Steals Comparison
```{r}
# How does his steals average compare to his teammates 
renderPlot({
  create_stat_plot("STL")
})
```


### Turnovers Comparison
```{r}
# How does his turnovers average compare to his teammates 
renderPlot({
  create_stat_plot("TOV")
})
```


Row
-----------------------------------------------------------------------

### Player Usage
```{r}
renderPlot({
  
  df <- roster() %>% 
      mutate(PlayerSelected = if_else(PLAYER_NAME == input$players, 
                                      "Selected", "Not Selected"))
  
  half <- round(max(df$GP) / 2)
  
  ggplot(df, aes(x = MIN, y = GP, color = PlayerSelected)) +
    geom_point() +
    geom_text_repel(aes(label = PLAYER_NAME), nudge_x = 0.5, nudge_y = 0.5) +
    geom_hline(yintercept = half, linetype = "dotted", size = .6) +
    geom_vline(xintercept = 20, linetype = "dotted", size = .6) +
    scale_fill_manual(values = c("Selected" = "#6F263D", "Not Selected" = "#1d428a")) +
    labs(x = "Minutes per game", y = "Games played") +
    theme(legend.position = "none") +
    theme_minimal()
    
})
```


TEAM SUMMARY {data-navmenu="SUMMARY"}
=======================================================================

```{r}
# Choose the proper team data set according to the selection
team_df <- reactive({
  if (current()$CONFERENCE == "East") {
    east %>% filter(TEAM_NAME == input$teams)
  } else {
    west %>% filter(TEAM_NAME == input$teams)
  }
})

# Choose the proper conference team data set according to the selection
conf_df <- reactive({
  if (current()$CONFERENCE == "East") {
    east 
  } else {
    west 
  }
})
```


Row
-----------------------------------------------------------------------
### Conference
```{r}
# What's the team's conference 
renderValueBox({
  valueBox(
    value = team_df()$CONFERENCE,
    caption = "Conference",
    icon = "fa-compass",
    color = "#1d428a"
  )
})
```


### Games Played
```{r}
# What's the number games played 
renderValueBox({
  valueBox(
    value = team_df()$GP,
    caption = "Games Played",
    icon = "fa-calendar-check",
    color = "#1d428a"
  )
})
```


### Win Percentage
```{r}
# What's the ratio of wins 
renderValueBox({
  valueBox(
    value = 100 * team_df()$W_PCT,
    caption = "% Wins",
    icon = "fa-trophy",
    color = "#1d428a"
  )
})
```


### Points per Game
```{r}
# How many points it averages
renderValueBox({
  valueBox(
    value = team_df()$PTS,
    caption = "Points Per Game",
    icon = "fa-basketball",
    color = "#1d428a"
  )
})
```


Row
-----------------------------------------------------------------------

### Field Goal Percentage
```{r}
# What's its field goal (2 points + 3 points) percentage 
renderGauge({
  gauge(value = 100 * team_df()$FG_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(40, 100), warning = c(20, 40), danger = c(0, 20),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


### Free Throw Percentage
```{r}
# What's its free throw percentage 
renderGauge({
  gauge(value = 100 * team_df()$FT_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(75, 100), warning = c(60, 75), danger = c(0, 60),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


### 3 Points Percentage
```{r}
# What's its 3 points percentage 
renderGauge({
  gauge(value = 100 * team_df()$FG3_PCT,
      min = 0,
      max = 100,
      symbol = '%', 
      gaugeSectors(success = c(35, 100), warning = c(20, 35), danger = c(0, 20),
                   colors = c("#0c4e24", "#FDBB30", "#ce1141"))
  )
})
```


Row
-----------------------------------------------------------------------

### Assists per Game 
```{r}
# How many assists it averages per game
renderValueBox({
  valueBox(
    value = team_df()$AST,
    caption = "Assists Per Game",
    icon = "fa-handshake-angle",
    color = "#1d428a"
  )
})
```


### Rebounds per Game 
```{r}
# How many rebounds it averages per game
renderValueBox({
  valueBox(
    value = team_df()$REB,
    caption = "Rebounds Per Game",
    icon = "fa-hands-holding-circle",
    color = "#1d428a"
  )
})
```


### Blocks per Game
```{r}
# How many blocks it averages per game
renderValueBox({
  valueBox(
    value = team_df()$BLK,
    caption = "Blocks Per Game",
    icon = "fa-hand-point-up",
    color = "#1d428a"
  )
})
```


### Steals per Game
```{r}
# How many steals it averages per game
renderValueBox({
  valueBox(
    value = team_df()$STL,
    caption = "Steals Per Game",
    icon = "fa-people-robbery",
    color = "#1d428a"
  )
})
```


### Turnovers per Game
```{r}
# How many turnovers it averages per game
renderValueBox({
  valueBox(
    value = team_df()$TOV,
    caption = "Turnovers Per Game",
    icon = "fa-person-walking-arrow-loop-left",
    color = "#1d428a"
  )
})
```

Row {.tabset}
-----------------------------------------------------------------------

### Points Comparison
```{r}
renderPlot({
  create_team_stat_plot("PTS")
})
```


### Assists Comparison
```{r}
renderPlot({
  create_team_stat_plot("AST")
})
```


### Rebounds Comparison
```{r}
renderPlot({
  create_team_stat_plot("REB")
})
```


### Blocks Comparison
```{r}
renderPlot({
  create_team_stat_plot("BLK")
})
```


### Steals Comparison
```{r}
renderPlot({
  create_team_stat_plot("STL")
})
```


### Turnovers Comparison
```{r}
renderPlot({
  create_team_stat_plot("TOV")
})
```




OFFENSE {data-navmenu="Under Development"}
=======================================================================

This tab is currently under development. Stay tuned!

Row
-----------------------------------------------------------------------

<!-- ### Minutes per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$MIN, -->
<!--     caption = "Minutes Per Game", -->
<!--     icon = "fa-clock", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### Points per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$PTS, -->
<!--     caption = "Points Per Game", -->
<!--     icon = "fa-basketball", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### Field Goal Attempted per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$FGA, -->
<!--     caption = "FG Attempted Per Game", -->
<!--     icon = "fa-dribbble", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### 3 Points Attempted per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$FG3A, -->
<!--     caption = "3 Pts Attempted Per Game", -->
<!--     icon = "fa-hands-asl-interpreting", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


<!-- ### Free Throws Attempted per Game  -->
<!-- ```{r} -->
<!-- renderValueBox({ -->
<!--   valueBox( -->
<!--     value = current()$FTA, -->
<!--     caption = "FT Attempted Per Game", -->
<!--     icon = "fa-ring", -->
<!--     color = "#1d428a" -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->


DEFENSE {data-navmenu="Under Development"}
=======================================================================

This tab is currently under development. Stay tuned!

Row
-----------------------------------------------------------------------

LEADERS
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### Points
```{r}
# What are the to 10 scorers 
renderPlotly({
  create_top_10("PTS")
})
```


### Assists
```{r}
# What are the to 10 passers
renderPlotly({
  create_top_10("AST")
})
```


### Turnovers
```{r}
# What are the to 10 careless ball-handlers
renderPlotly({
  create_top_10("TOV")
})
```


### Rebounds
```{r}
# What are the to 10 rebounders
renderPlotly({
  create_top_10("REB")
})
```


### Blocks
```{r}
# What are the to 10 deniers
renderPlotly({
  create_top_10("BLK")
})
```


### Steals
```{r}
# What are the to 10 active hands
renderPlotly({
  create_top_10("STL")
})
```


Row
-----------------------------------------------------------------------

### Western Ranking
```{r}
# What's the ranking in the west
renderPlotly({
  create_ranking(west)
})
```


### Eastern Ranking
```{r}
# What's the ranking in the east
renderPlotly({
  create_ranking(east)
})
```

